Tensor anisotropy as a tracer of cosmic voids

### 2015-03-04 cosmic_voids.tex
revision de abstract, conclusiones y caption

\begin{abstract}
We present a new method to find voids in cosmological simulations
based on algorithms that use the tidal and the velocity shear tensors
to locally define the cosmic web. 
We show that fractional anisotropy (FA) computed from the eigenvalues
of each web scheme is a good void tracer. 
Based on this result we identify voids using a watershed
transform based on the local minima of the FA field.
This void identification technique does not make any assumption on the
shape or structure of the voids. 
We test the method on the Bolshoi simulation and report on the
abundance and radial averaged profiles for the density, velocity and
fractional anistropy.
We find that voids in the velocity shear web are smaller than voids in
the tidal web, with a particular overabundance of very small voids in
the inner region of filaments/sheets.
We clasify voids as subcompensated/overcompansated depending on the
absence/presence of an overdense matter ridge in their density
profile, finding that close to $65\%$ and $35\%$ of the total
population are classified into each category, respectively.
Finally, we find evidence for the existence of universal profiles once the
radial coordinate is normalized to the effective radius of each void
from the radiallly averaged profiles for density, velocity and
fractional anisotropy. 
\end{abstract}

@@

Cosmic voids are one of the most striking features of the
Universe on its larges scales since they were found in the first
galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87}.  
However, due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through modern galaxy surveys such as the two-degree field Galaxy
Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
These observational breakthroughs generated a great interest in the last
decade to study voids \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Visual impression of different results mentioned in this
    paper for a slice of $1\hMpc$ width in the Bolshoi simulation.  
    Fractional Anisotropy field (left); cosmic web classification
    (middle) where voids are white, sheets are light gray, filaments
    are dark gray and knots are black; and colored individual
    voids found by the a watershed algorithm on the Fractional
    Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
    over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include $50\%$ of all
    cells. 
    This information is necesary to define void boundaries in
    the watershed algorithm. 
    The vertical lines show the equivalent threshold values for the
    T-Web and V-web in order to have voids composed by cells with
    Fractional Anisotrop equal or less than $0.95$.}
  \label{fig:L1_correlations}

@@

We propose in this paper that the anisotropy of the eigenvalues from
tensors constructed to describe the cosmic web is a good tracer of
cosmic voids. Based on this idea we go on to implement a watershed
algorithm o the fractional anisotropy to find voids voids in a N-body
cosmological simulations. We perform this tests on the results of two
different tensorial schemes, the T-Web and the V-web.

The first quantity we take a look at is the void size distribution
characterized by an effective radius. 
We find that for T-Web voids the shape of this function corresponds to
standard expectations. 
However, for the V-Web we find an overabundance of the smallest voids
due to artifacts in the web finding scheme in sheets and small
fragmented voids inside the largest voids already identified in the
T-Web, perhaps due to the complex velocity structure in large voids
compared to a simpler density/gravitational potential anatomy.

A second step in the characterization of the voids found by our method
was the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated, meaning that
they are located in denser regions with a clear delimiting ridge. 
For the V-web the subcompensated fraction increases from $65\%$ to
$85\%$ as the void size decreases, supporting the picture of smaller
spurious voids located in low density matter sheets.

Finally we proceed with an ever more detailed void characterization
through the radially averaged profiles of density, radial velocity and
fractional anisotropy. 
In thi case we studied separately the subcompensated and
overcompensated voids, split this time in samples with different
effective radii.

In the density profiles the most interesting feature is that the 
profile has a similar shape for all the different void sizes once the
radial coordinate is expressed in units of the effective radius. 
In these profiles it is evident the presence of an overdense ridge
around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/r_{\rm eff}\sim 8$.

@@

The velocity profiles show the expected correlation with the features
already observed in the density, most notably the radial velocity goes to
zero close to flat regions in the density profile and is positive around
regions of increasing density with radius.

>>>>

\begin{abstract}
We present a new method to find voids in cosmological simulations
based on the tidal and the velocity shear tensors
definitions of the cosmic web. 
We use the fractional anisotropy (FA) computed from the eigenvalues
of each web scheme as a void tracer.
We identify voids using a watershed transform based on the local
minima of the FA field without making any assumption on the shape or
structure of the voids.  
We test the method on the Bolshoi simulation and report on the
abundance and radial averaged profiles for the density, velocity and
fractional anistropy.
We find that voids in the velocity shear web are smaller than voids in
the tidal web, with a particular overabundance of very small voids in
the inner region of filaments/sheets.
We clasify voids as subcompensated/overcompansated depending on the
absence/presence of an overdense matter ridge in their density
profile, finding that close to $65\%$ and $35\%$ of the total
population are classified into each category, respectively.
Finally, we find evidence for the existence of universal profiles once the
radial coordinate is normalized to the effective radius of each void
from the radiallly averaged profiles for density, velocity and
fractional anisotropy. 
Put together, all these results show that the FA is a reliable tracer
for voids, which can be used in complementarity to other existing
methods and tracers.
\end{abstract}

@@

Cosmic voids are one of the most striking features of the
Universe on its larges scales ever since they were found in the first
galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87}.  
However, due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through modern galaxy surveys such as the two-degree field Galaxy
Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
These observational breakthroughs generated a great interest in the last
decade to study voids \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Visual impression of different fields in a slice of
    $1\hMpc$ width in the Bolshoi simulation.   
    Fractional Anisotropy field (left); cosmic web classification
    (middle) where voids are white, sheets are light gray, filaments
    are dark gray and knots are black; colored individual
    voids (right) found by the a watershed algorithm on the Fractional
    Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
    over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin.
    This information is necesary to define void boundaries in
    the watershed algorithm. 
    The vertical lines show the equivalent threshold values for the
    T-Web and V-web in order to have voids composed by cells with
    Fractional Anisotrop equal or less than $0.95$.}
  \label{fig:L1_correlations}

@@

In this paper we propose that the anisotropy of the eigenvalues from
tidal and velocity shear tensors is a good tracer of  cosmic voids. 
Based on this idea we go on to implement a watershed
algorithm o the fractional anisotropy to find voids in a N-body
cosmological simulation.
We perform different test on the voids found on the anisotropy of two
tensorial schemes, the T-Web and the V-web.

The first quantity examine is the void size distribution
characterized by an effective radius. 
We find that for T-Web voids the shape of this function corresponds to
standard expectations from a two-barrier setup. 
However, for the V-Web we find an overabundance of the smallest voids.
This is due to artifacts in the web finding scheme in sheets and also
to the smaller fragmented voids inside the largest voids already
identified in the T-Web. 
The void fragmentation hints at a complex velocity structure in large
voids compared to its simpler density/gravitational potential anatomy.

A second step in the characterization of the voids found by our method
is the separation into subcompensated and overcompensated samples. 
In the T-Web $35\%$ of the voids are overcompensated ($65\%$
subcompensated), meaning that they are located in denser regions with
a clear delimiting ridge.   
For the V-web the subcompensated fraction rises from $65\%$ to $85\%$ as the
void size decreases, supporting the picture of smaller spurious voids
located in low density matter sheets.

Finally we proceed with an more detailed void characterization
through the radially averaged profiles of density, radial velocity and
fractional anisotropy. 
In this case we study separately the subcompensated and
overcompensated voids, split this time in samples with different
effective radii.

For the density the most interesting feature is that the  profile has
a similar shape for all the different void sizes once the radial
coordinate is expressed in units of the effective radius.  
In these profiles it is evident the presence of an overdense ridge
around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/r_{\rm eff}\sim 8$.

@@

The velocity profiles show the expected correlation with the features
already observed in the density.
Most notably the radial velocity goes to zero close to flat regions in
the density profile and is positive around regions of increasing
density with radius.
